Equivalence Testing and the Second Generation P-Value

### 2018-07-18 sgpv_vs_TOST.Rmd
make github doc

---
title: "Equivalence Testing and the Second Generation P-Value"
author: "Daniël Lakens & Marie Delacre"
date: "1 juli 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Equivalence Testing and the Second Generation P-Value"
author: "Daniël Lakens & Marie Delacre"
date: "1 juli 2018"
output: github_document
---
